The College Application Problem

### 2022-05-03 slides_08min/slides.tex
split slides into 8- and 20-minute versions; translations

\newif\ifen\enfalse
% Language selector; must be on line 3
% Change to false to export Korean

@@

\ifen 
\title{The College Application Problem}
\author{Max Kapur and Sung-Pil Hong}
\institute{Seoul National University\\
Department of Industrial Engineering \\
Management Science/Optimization Lab}
\date{\today}
\else
\title[대학 지원 최적화 문제]{대학 지원 최적화 문제}
\author{Max Kapur \& 홍성필}
\institute{서울대학교\\
산업공학과 \\
경영과학/최적화 연구실}
\date{\today}
\fi

@@

\textbf{Maximize the expected maximum} of a portfolio of random variables subject to a budget constraint.

Today's agenda:
\begin{itemize}
\item \textbf{Formulate} college application as an optimization problem.
\item The \textbf{status quo} in admissions consulting, and why common heuristics fall short.
\item Our theoretical results, \textbf{solution algorithms}, and Julia implementation.
\end{itemize}

\textbf{Proofs and additional results} in our arXiv paper (Kapur and Hong 2022). 
\end{frame}
} \else {
\begin{frame}{서론}
대학 지원 최적화 문제란 \textbf{새로운 조합 최적화 문제}이다.

@@

발표 요약:
\begin{itemize}
\item 대학 지원 전략을 최적화 문제로 \textbf{모형화}.
\item \textbf{현재 상황}: 입학 컨설팅 산업에서 흔히 사용하는 휴리스틱의 부족함.
\item 본 연구가 제시하는 \textbf{이론적 결과, 해법, 알고리즘 구현}.
\end{itemize}
\end{frame}
} \fi

\ifen {
\begin{frame}{Methodological orientation}
College application spans several areas of combinatorial optimization:

\begin{itemize}
\item Investment with uncertain payoff, search for the efficient frontier recall \textbf{portfolio allocation} models. 
\item Generalizes the \textbf{knapsack problem}: Integral packing constraint, NP-completeness.
\item Objective is a \textbf{submodular set function}, but approximation results suggest college application is a relatively easy instance. 
\end{itemize}
\end{frame}
} \else {
\begin{frame}{방법론적 지향}
대학 지원 전략은 조합 최적화 중 여러 분야를 걸친다.

\begin{itemize}
\item 불확실한 성과, 효율적 투자선이 존재하는 일종의 \textbf{포트폴리오 배분} 모형. 
\item \textbf{배낭 문제}의 일반화: 정수 패킹 제약식, NP-completeness.
\item 목적함수는 \textbf{submodular 집합 함수}이며, 근사 해법 결과에 따라 대학 지원 문제가 submodular 최적화의 비교적 쉬운 인스턴스로 해석할 수 있다.
\end{itemize}
\end{frame}

} \fi

@@

\ifen {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
~
\end{center}
\end{frame}
} \else {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
~
\end{center}
\end{frame}
} \fi

@@

어떤 대학에도 합격 안 하면 효용이 $t_0$이며, wlog $t_0 =0$임을 가정할 수 있다 (논문 참고).

@@

\ifen \section{The status quo} \else \section{기존의 해법} \fi

\ifen {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \else {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \fi

\begin{frame}[plain]%{Safety, target, and reach schools}
\vfill

@@

\ifen Can we trust the admissions consultant's advice?
\else 입학 컨설턴트의 조언, 믿을 만하는가? \fi
\end{center}

@@

\begin{frame}[plain]{}
\begin{center}
\includegraphics[height=\textheight]{plots/samplemarket.pdf}
\end{center}
\end{frame}

\begin{frame}[plain]{}
\begin{center}
\includegraphics[height=\textheight]{plots/samplemarket-soln.pdf}
\end{center}
\end{frame}

\begin{frame}{Existing solutions}

In practice, most use \textbf{distributive heuristics} such as distributing applications evenly among attractive, selective ``reach schools'' and less-attractive ``safety schools.'' Turns out to be a \textbf{risk-averse} approach.

@@

Our algorithms provide both \textbf{time and accuracy guarantees}.

\ifen \section{Our algorithms} \else \section{제시 알고리즘} \fi

\ifen {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \else {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \fi

\ifen {
\begin{frame}{Homogeneous costs: A polynomially solvable case}
We first consider the \textbf{special case} in which each $g_j = 1$ and $H$ is simply $h \leq m$, a limit on the number of schools you can apply to.

This case mirrors the main Korean admissions cycle, in which $h = 3, m= 202$.

We show that when $\mathcal{X}_h$ is the optimal portfolio at $h$, $\mathcal{X}_{h} \subset \mathcal{X}_{h+1}$. This \textbf{nestedness property} implies the optimality of a \textbf{greedy algorithm} that adds schools one at a time, maximizing $v(\mathcal{X})$ at each addition.

Using a variable-elimination technique, we reduce the cost of computing $v(\mathcal{X})$ to amortized unit time, obtaining an $O(hm)$ algorithm. Our Julia implementation (Kapur 2022) solves an $m = 16384$ instance in 200 ms.

Strengthens the result of Fisher et al. (1978). 
\end{frame}
} \else {
\begin{frame}{다항 시간에 풀 수 있는 동일한 지원 비용의 경우}
먼저 모든 $g_j = 1$이며 $H$는 단순한 지원 개수 제한 $h \leq m$이 되는 \textbf{특수한 경우}를 고려하자.

이것은 $h = 3, m= 202$인 한국 정시 입학 과정과 비슷한 상황이다.

지원 제한 $h$에 대응되는 최적 포트폴리오가 $\mathcal{X}_h$일 때, $\mathcal{X}_{h} \subset \mathcal{X}_{h+1}$을 증명할 수 있다. 이러한 \textbf{포함 사슬 관계 (nestedness)} 성질은 $v(\mathcal{X})$를 최대화하는 순서대로 학교를 하나씩 추가하는 \textbf{탐욕 해법}의 최적성을 의미한다.

변수 소거 기법은 개발하여 $v(\mathcal{X})$를 계산하는 시간을 환산 단위 시간을 줄임으로 $O(hm)$ 해법을 얻을 수 있다. 쥴리아 코드(Kapur 2022)를 사용하면 $m = 16384$인 인스턴스를 200 ms에 풀 수 있다.

Fisher et al. (1978)에 결과를 강화한다.
\end{frame}
} \fi

\ifen {
\begin{frame}{A small example}
College data and optimal application portfolios for a fictional market with $m=8$ schools.
\vspace{-1em}
\begin{center}
\begin{tabular}{r|lcccc}
\textbf{$j$} & \textbf{School $c_j$} & \textbf{Admit prob. $f_j$} & \textbf{Utility $t_j$} & \textbf{Priority} & \textbf{$v(\mathcal{X}_h)$} \\ \hline
\\[-.75em]
1 & Mercury University  & 0.39   & 200 & 4   & 230.0   \\
2 & Venus University    & 0.33   & 250 & 2   & 146.7  \\
3 & Mars University     & 0.24   & 300 & 6   & 281.5  \\
4 & Jupiter University  & 0.24   & 350 & 1   & \phantom{0}84.0  \\
5 & Saturn University   & 0.05   & 400 & 7   & 288.8  \\
6 & Uranus University   & 0.03   & 450 & 8   & 294.1  \\
7 & Neptune University  & 0.10   & 500 & 5   & 257.7  \\
8 & Pluto College       & 0.12   & 550 & 3   & 195.1      
\end{tabular}
\end{center}
By the nestedness property, the optimal portfolio when the application limit is $h$ consists of the $h$ schools having priority $h$ or less.

Valuation function appears on next slide. Always concave.
\end{frame}
} \else {
\begin{frame}{작은 예제}
$m=8$개의 학교로 이루어진 가상 입학 시장의 대학교 자료와 최적 지원 포트폴리오.
\begin{center}
\begin{tabular}{r|lcccc}
\textbf{지표 $j$} & \textbf{학교 $c_j$} & \textbf{합격 확률 $f_j$} & \textbf{효용 $t_j$}  & \textbf{지원 순위} & \textbf{$v(\mathcal{X}_h)$} \\ \hline
\\[-.75em]
1 & 수성대   & 0.39   & 200 & 4   & 230.0   \\
2 & 금성대   & 0.33   & 250 & 2   & 146.7  \\
3 & 화성대   & 0.24   & 300 & 6   & 281.5  \\
4 & 목성대   & 0.24   & 350 & 1   & \phantom{0}84.0  \\
5 & 토성대   & 0.05   & 400 & 7   & 288.8  \\
6 & 천왕성대  & 0.03   & 450 & 8   & 294.1  \\
7 & 해왕성대  & 0.10   & 500 & 5   & 257.7  \\
8 & 명왕성대  & 0.12   & 550 & 3   & 195.1      
\end{tabular}
\end{center}
포함 사슬 관계 성질에 따라, 지원 제한이 $h$일 때 최적 포트폴리오는 지원 순위가 $h$ 이하인 $h$개의 학교로 구성된다.
\end{frame}
} \fi

\begin{frame}[plain]
\begin{center}
 \includegraphics[height=\textheight]{./plots/h_v-example.pdf}
\end{center}
\end{frame}

\begin{frame}{Algorithms for the general problem}
The general problem is \textbf{NP-complete} (reduction from knapsack). We offer four algorithms:
\begin{itemize}
\item A linear relaxation and \textbf{branch-and-bound scheme}. Primarily of theoretical interest.

@@

\item A different DP based on truncated portfolio valuations. $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time: an \textbf{FPTAS}!
\item A \textbf{simulated annealing heuristic}. Fast, typically within 2\% of optimality.
\end{itemize}

Existence of FPTAS suggests college application is \textbf{a relatively easy instance of submodular maximization} (cf. Kulik et al. 2013).
\end{frame}

\ifen \section{Conclusion} \else \section{결론} \fi

\ifen {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \else {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \fi

\begin{frame}{Conclusion}
``Maximax form,'' integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack.

The nestedness result for the $g_j = 1$ special case also resembles the knapsack problem, although the proof is more subtle.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, memory-usage improvements.
\end{frame}

\begin{frame}[allowframebreaks]{\ifen References \else 참고 문헌 \fi}
\scriptsize
\parskip 0em
\leftskip 2em
\parindent -2em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

@@

Fisher, Marshall, George Nemhauser, and Laurence Wolsey. 1978. ``An analysis of approximations for maximizing submodular set functions—I.'' \emph{Mathematical Programming} 14: 265--94.

@@

Kapur, Max and Sung-Pil Hong. 2022. ``The Optimal College Application Problem.'' Preprint. \url{https://github.com/maxkapur/CollegeApplication}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{\ifen Introduction\else 서론 \fi}
\ifen {
The optimal college application problem is a \textbf{novel combinatorial optimization problem}.

Our methodological orientation:
\begin{itemize}
\item \textbf{Asset allocation perspective:} Valuation vs. value, inherent risk/reward tradeoff, efficient frontier.
\item \textbf{Knapsack perspective:} Integrality constraint, dynamic programming solutions, NP-completeness, approximation algorithms.
\end{itemize}
} \else {

방법론적 지향:
\begin{itemize}
\item \textbf{자산배분 최적화 관점:} 가치 (valuation) vs. 가치 (value), 위험/보상 관리, 효율적 투자선.
\item \textbf{배낭 문제 관점:} 정수 조건, 동적 계획, NP-completeness, 근사 해법.
\end{itemize}
} \fi
\end{frame}

\begin{frame}{\ifen The college application process\else 대학 지원 과정\fi}
\ifen Consider a student deciding where to apply to college. 
\else 대학 지원 전략을 고민하는 학생을 고려하자. \fi

\ifen There are $m$ schools, $\mathcal{C} = \{ 1 \dots m\}$. The $j$th school is named $c_j$.
\else $m$개의 학교, $\mathcal{C} = \{ 1 \dots m\}$. $j$번째 학교의 이름은 $c_j$. \fi

\ifen $t_j > 0$: \textbf{Utility} from attending $c_j$. Receive $t_0$ units of utility if she gets in nowhere.  Wlog, $t_0 < t_1 \leq \cdots \leq t_m$. 
\else 학생이 $c_j$에 다니면 그의 효용은 $t_j > 0$이며 대학에 못가면 $t_0$. Wlog, $t_0 < t_1 \leq \cdots \leq t_m$. \fi

\ifen $f_j \in (0, 1]$: \textbf{Probability of getting into} $c_j$ if she applies. $f_0 = 1$. Admissions outcome is $Z_j \sim \operatorname{Bernoulli}(f_j)$. 
\else $f_j \in (0, 1]$: 학생이 $c_j$에 지원할 때, 그의 \textbf{합격 확률}. $f_0 = 1$. 합격 결과는 $Z_j \sim \operatorname{Bernoulli}(f_j)$. \fi

\ifen $\mathcal{X}$: Student's \textbf{application portfolio}, the set of schools to which she chooses to apply. 
\else $\mathcal{X}$: 학생의 \textbf{지원 포트폴리오}, 즉 지원하는 학교의 집합.\fi

\ifen $p_j(\mathcal{X})$: \textbf{Probability that student attends} $c_j$. For $j= 0 \dots m$,
\else $p_j(\mathcal{X})$: 학생이 $c_j$에 \textbf{진학할 확률}. $j= 0 \dots m$에 대해,\fi
\begin{align*}
p_j(\mathcal{X}) &= 
\begin{cases}
\displaystyle f_j  \prod_{\substack{j’ \in \mathcal{X}: \\ j' > j}} (1 - f_{j’}), \quad & j \in \{0\}\cup\mathcal{X}\\
0, \quad & \text{otherwise.}
\end{cases} 
\end{align*}
\end{frame}

\begin{frame}{\ifen Objective function and constraints\else 목적함수와 제약 조건\fi}
\ifen {
The student's objective is to maximize her expected utility, which is the expected value of the \textbf{best} school she gets into. Notice the ``maximax'' form.
\begin{align*}
v(\mathcal{X})
&= \operatorname{E}\Bigl[\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
&= \sum_{j=0}^m t_j p_j(\mathcal{X}) = \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)  \label{closedformportfoliovaluationX}%, \quad \text{or equivalently,}\\
%\qquad v(x) &= t_0 \prod_{j=1}^m (1 - f_{j} x_j) + \sum_{j=1}^m \Bigl( x_j t_j f_j \prod_{j’ = j+1}^m (1 - f_{j’} x_{j’}) \Bigr) \label{closedformportfoliovaluationx}
\end{align*}
(As we show, wlog to assume $t_0 = 0$.)

We consider two kinds of constraints:
\begin{itemize}
\item \textbf{Cardinality constraint}: A limit $h$ on the number of applications, as in Korea's college admissions process. ``Alma's problem,'' solvable in polynomial time.
\item Application \textbf{budget constraint}: Each school has application cost $g_j$, and student has $H$ units to spend on applications. ``Ellis's problem,'' NP-complete.
\end{itemize}
}\else{
학생의 목적은 자신이 기대 효용을 최대화하는 것이며 이는 합격하는 학교 중 효용이 \textbf{최대}인 학교이다. 목적함수의 ``maximax'' 형태는 본 모형의 특색.
\begin{align*}
v(\mathcal{X})
&= \operatorname{E}\Bigl[\max\bigr\{t_0, \max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
&= \sum_{j=0}^m t_j p_j(\mathcal{X}) = \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)  \label{closedformportfoliovaluationX}%, \quad \text{or equivalently,}\\
%\qquad v(x) &= t_0 \prod_{j=1}^m (1 - f_{j} x_j) + \sum_{j=1}^m \Bigl( x_j t_j f_j \prod_{j’ = j+1}^m (1 - f_{j’} x_{j’}) \Bigr) \label{closedformportfoliovaluationx}
\end{align*}
(논문에서 보이듯이, $t_0 = 0$이라고 가정할 수 있다.)

2가지의 제약 조건 형태를 고려한다.
\begin{itemize}
\item \textbf{집합 크기 제약}: 한국 정시 입학 과정처럼 지원할 수 있는 학교의 개수가 $h$로 제한된 ``알마의 문제.'' 다항 시간 해법 존재.
\item \textbf{지원 비용 예산 조건}: 각 학교의 지원 비용이 $g_j$이며 학교가 지원에 쓸 수 있는 금액이 $H$인 ``엘리스의 문제.'' NP-complete.
\end{itemize}
}\fi
\end{frame}

\begin{frame}{\ifen Problem statement\else 문제 정의 \fi}
\begin{problem}[\ifen Alma’s problem\else 알마의 문제\fi]
\vspace{-1em}
%\ifen Alma's optimal college application portfolio is given by the solution to the following combinatorial optimization problem:
%\else
%알마의 최적 대학 지원 포트폴리오는 다음 조합 최적화 문제의 최적해이다.
%\fi
\begin{align*}
\begin{split}
\text{maximize}\quad &  v(\mathcal{X}) = \sum_{j\in
%\{0\}\cup
\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)\\
\text{subject to}\quad & \mathcal{X}\subseteq\mathcal{C}, \quad|\mathcal{X}| \leq h 
\end{split}
\end{align*}
\end{problem}
\begin{problem}[\ifen Ellis's problem\else 엘리스의 문제\fi]
\vspace{-1em}
%\ifen
%Ellis's optimal college application portfolio is given by the solution to the following combinatorial optimization problem.
%\else 
%엘리스의 최적 대학 지원 포트폴리오는 다음 조합 최적화 문제의 최적해이다.
%\fi
\begin{align*}
\begin{split}
\text{maximize}\quad &  v(\mathcal{X}) = \sum_{j\in
%\{0\}\cup
\mathcal{X}} \Bigl(f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)\\
\text{subject to}\quad & \mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H 
\end{split}
\end{align*}
\end{problem}

\ifen Set all $g_j = 1$ to see that Alma's problem is a special case of Ellis's problem. 
\else 모든 $g_j = 1$로 넣으면 알마의 문제가 엘리스의 문제의 특수한 경우임을 알 수 있다.  \fi
\end{frame}

\begin{frame}{\ifen Why college application is difficult\else 대학 지원 문제가 왜 어려운가\fi}
\ifen
``Obvious'' algorithm which picks the schools having highest expected value $f_j t_j$ is \textbf{incorrect.} ($\tfrac{1}{h}$-opt. for Alma’s problem; $\tfrac{1}{m-1}$-opt. for Ellis’s problem.)

College application can be expressed as a nonlinear integer program, but it is \textbf{not concave}.

\textrightarrow~Problem is \textbf{combinatorial} in nature.

Typical instances (see following slide) involve \textbf{negative correlation} between probabilities $f_j$ and utility values $t_j$.

\textrightarrow~Students must trade off attractive, selective “reach schools” against less preferable “safety schools” where admission is a safer bet.

A good application strategy has \textbf{monetary value}. US admissions consultants charge an average of \$200/hr (Sklarow 2018).

Previous research considered small ($m=8$) instances and solved by enumeration (Chao 2014).
\else
기대 가치 $f_j t_j$가 가장 큰 학교를 선택하는 `뻔한' 알고리즘은 사실 틀리다. (근사 계수는 알마 문제에 대해 $\tfrac{1}{h}$, 엘리스 문제에 대해 $\tfrac{1}{m-1}$.)

정수 비선형 계획으로 표현할 수 있지만 목적함수가 \textbf{오목}이 아니다.

\textrightarrow~본성적으로 \textbf{조합적인} 문제.

%\textbf{알마의 문제는 다항 시간} 안에 풀 수 있지만, 기대 가치 $f_j t_j$가 가장 큰 $h$개의 학교를 선택하는 `뻔한' 알고리즘은 사실 틀리다.

%\textbf{엘리스의 문제는 NP-complete}하며 배낭 문제에서 변환함으로 증명.

전형적인 인스턴스(다음 화면)에서 입학 확률 $f_j$와 효용 모수 $t_j$가 서로 \textbf{반비례}한다.

\textrightarrow~선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다고 의미.

좋은 지원 전략은 \textbf{금전적인 가치}를 가진다. 미국 입학 상담가의 시간당 급료는 평균 24만원 (Sklarow 2018).

선행 연구는 작은 ($m=8$) 인스턴스만 고려하고 열거법으로 풀었다 (Chao 2014).
\fi
\end{frame}

% Reverse order of slides in Korean version
\ifen 
\begin{frame}[plain]{}
\begin{center}
\includegraphics[width=\textwidth]{plots/news-en.png}
\end{center}
\end{frame}
\fi

\begin{frame}[plain]{}
\begin{center}
\includegraphics[width=\textwidth]{plots/news-ko.png}
\end{center}
\end{frame}

\ifen \else
\begin{frame}[plain]{}
\begin{center}
\includegraphics[width=\textwidth]{plots/news-en.png}
\end{center}
\end{frame}
\fi

\begin{frame}[plain]{}
\begin{center}
\includegraphics[height=\textheight]{plots/samplemarket.pdf}
\end{center}
\end{frame}

\begin{frame}[plain]{}
\begin{center}
\includegraphics[height=\textheight]{plots/samplemarket-soln.pdf}
\end{center}
\end{frame}

\ifen \section{Alma's problem} \else \section{알마의 문제} \fi

\ifen{
\begin{frame}[plain]
  \vspace{9em}
\begin{center}
~
\begin{beamercolorbox}[wd=.6\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead \par%
  \end{beamercolorbox}
~
\end{center}
\end{frame}
}
\else{
\begin{frame}
  \vspace{9em}
\begin{center}
~
\begin{beamercolorbox}[wd=.6\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead \par%
  \end{beamercolorbox}
~
\end{center}
\end{frame}
}
\fi

\begin{frame}{\ifen The nestedness property for Alma's problem\else 알마 문제 최적해의 포함 사슬 관계\fi}
\ifen The following theorem says that the solution to Alma's problem is \textbf{nested} in the application limit $h$.
\else 다음 정리는 알마 문제의 최적해가 지원 제한 $h$로 모수화된 \textbf{포함 사슬 관계}를 가진다고 의미한다. \fi
\begin{theorem}[\ifen Nestedness of optimal application portfolios\else 최적 포트폴리오의 포함 사슬 관계\fi] \label{nestedapplication}
\ifen There exists a sequence of portfolios $\{\mathcal{X}_h\}_{h=1}^m$ satisfying the nestedness relation
\else  각 $\mathcal{X}_h$가 지원 제한 $h$에 대한 최적 포트폴리오며 위의 포함 사슬 관계를 만족하는 포트폴리오 수열  $\{\mathcal{X}_h\}_{h=1}^m$가 존재한다.\fi
\begin{equation*}
\mathcal{X}_1 \subset \mathcal{X}_2\subset \dots \subset \mathcal{X}_m
\end{equation*}
\ifen such that each $\mathcal{X}_h$ is an optimal application portfolio when the application limit is $h$.\fi
\end{theorem}

\ifen
This implies the validity of a greedy algorithm that adds schools one at a time, maximizing $v(\mathcal{X})$ at each addition.

Some additional refinement reduces the computation time to $O(hm)$.
\else
따라서 $v(\mathcal{X})$를 최대화하는 학교를 차례대로 추가하는 탐욕 해법의 타당성이 성립.

이를 좀 더 조정하면 계산 시간을 $O(hm)$으로 절감할 수 있다.
\fi
\end{frame}

\begin{frame}{\ifen Concavity of $v(\mathcal{X}_h)$\else $v(\mathcal{X}_h)$의 오목성\fi}
\ifen The nestedness property implies that Alma's expected utility is a discretely concave function of $h$.
\else 포함 사슬 관계 성질은 알마의 기대 효용이 $h$의 이산 오목 함수임을 의미한다.\fi

\begin{theorem}[\ifen Optimal portfolio valuation concave in $h$\else 최적 포트폴리오 가치의 $h$-오목성\fi] \label{concavityinh}
\ifen For $h = 2 \dots (m-1)$,
\else $h = 2 \dots (m-1)$에 대해,\fi
\begin{equation*}v(\mathcal{X}_h) - v(\mathcal{X}_{h-1}) \geq v(\mathcal{X}_{h+1}) - v(\mathcal{X}_{h}).\end{equation*} 
\end{theorem}

\ifen
Corollary: $v(\mathcal{X}_h)$ is $O(h)$. Paper contains a tight example. 
\else
이의 따름정리로서 $v(\mathcal{X}_h)$가 $O(h)$ 함수가 되며, 논문에서 타이트한 예를 제시. 
\fi
\end{frame}

>>>>

\newif\ifen\entrue
% Language selector; must be on line 3
% Change to false to export Korean

@@

\ifen 
\title{The College Application Problem}
\author{Max Kapur}
\institute{Seoul National University\\
Department of Industrial Engineering \\
Management Science/Optimization Lab}
\date{\today}
\else
\title[대학 지원 최적화 문제]{대학 지원 최적화 문제}
\author{Max Kapur}
\institute{서울대학교\\
산업공학과 \\
경영과학/최적화 연구실}
\date{\today}
\fi

@@

It involves \textbf{maximizing the expected maximum} of a portfolio of random variables subject to a budget constraint.

Methodological orientation:
\begin{itemize}
\item Investment with uncertain payoff, search for the efficient frontier recall \textbf{portfolio allocation} models. 
\item Generalizes the \textbf{knapsack problem}: Integral packing constraint, NP-completeness, approximation algorithms.
\item Objective is a \textbf{submodular set function}.
\end{itemize}

Today's presentation: \textbf{define the problem} and briefly summarize our \textbf{solution algorithms}. 
\end{frame}
} \else {
\begin{frame}{서론}
대학 지원 최적화 문제란 \textbf{새로운 조합 최적화 문제}이다.

@@

방법론적 지향:
\begin{itemize}
\item 불확실한 성과, 효율적 투자선이 존재하는 일종의 \textbf{포트폴리오 배분} 모형. 
\item \textbf{배낭 문제}의 일반화: 정수 패킹 제약식, NP-completeness, 근사 해법.
\item 목적함수는 \textbf{submodular 집합 함수}.
\end{itemize}

오늘 발표에서는 \textbf{문제를 정의하고 본 연구가 제시하는 해법}을 요약한다. 
\end{frame}
} \fi

@@

@@

어떤 대학에도 합격 안 하면 효용이 $t_0$이며, wlog $t_0 =0$임을 가정할 수 있다 (논문에서 증명).

@@

\ifen \section{Solution} \else \section{해법} \fi

\begin{frame}%{Safety, target, and reach schools}
\vfill

@@

\ifen Do you trust the admissions consultant's advice?
\else 입학 컨설턴트의 조언, 믿을 만하는가? \fi
\end{center}

@@

\ifen {
\begin{frame}{Existing solutions}
In practice, most use \textbf{distributive heuristics} such as distributing applications evenly among reach, target, and safety schools. Turns out to be a \textbf{risk-averse} approach.

@@

Our algorithms provide both \textbf{time and accuracy guarantees}. 
\end{frame}
} \else {
\begin{frame}{기존의 해법}
입학 컨설팅 산업에서는 주로 ``상향·소신·안정 지원 학교'' 각각 균일하게 지원하는 \textbf{배분적 휴리스틱}을 사용하며, \textbf{위험 회피적인} 전략임을 알 수 있다.

또한 \textbf{선형화 휴리스틱}이 있다. $c_j$에만 지원할 때 기대 효용이 $f_j t_j$이므로 다음 배낭 문제를 대리 문제로 푼다.
\[\text{maximize}~~\sum_{j\in \mathcal{X}} f_j t_j \qquad \text{subject to}~~\sum_{j\in \mathcal{X}}g_j \leq H \]
이의 \textbf{근사 계수가 $\mathbf{0}$에 무한히 가까운} 예시를 만들 수 있다.

Fu (2014)는 비슷한 문제를 \textbf{열거법}으로 풀었으며, $m \geq 20$일 때 불현실적인 방법이다.

본 연구가 제시하는 알고리즘은 \textbf{계산 시간과 정확도를 보장한다}. 
\end{frame}
} \fi

\ifen {
\begin{frame}{Our algorithms}
In the \textbf{special case} where each $g_j = 1$, we provide an $O(m^2)$ algorithm.

The general problem is \textbf{NP-complete} (reduction from knapsack). We offer four algorithms:
\begin{itemize}
\item A linear relaxation and \textbf{branch-and-bound scheme}. Primarily of theoretical interest.

@@

\item A different DP based on truncated portfolio valuations. $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time: an \textbf{FPTAS}!
\item A \textbf{simulated annealing heuristic}. Fast, typically within 2\% of optimality.
\end{itemize}
\end{frame}
} \else {
\begin{frame}{제시 알고리즘}
모든 $g_j = 1$인 특수한 경우를 위한 $O(m^2)$ 알고리즘 제시.

일반적인 문제는 \textbf{NP-complete} (배낭 문제에서 변환). 4개의 알고리즘 제시:
\begin{itemize}
\item 선형 완화 문제와 해당 \textbf{branch-and-bound} 해법. 주로 이론적인 흥미가 있다.

\item \textbf{지원 지출액 기반 동적 계획}. (의사 다항) $O(Hm + m\log m)$ 시간에 정확한 해를 구하며, $g_j$가 작은 정수가 되는 ``전형적'' 인스턴스에 대해 매우 효율적인 해법.

\item 포트폴리오 가치의 라운딩을 이용한 다른 동적 계획. $O(m^3 / \varepsilon)$ 시간에 $(1 - \varepsilon)$-근사해를 출력하므로 \textbf{FPTAS}!
\item \textbf{Simulated annealing} 휴리스틱. 빠르고 거의 항상 최적의 2\% 이내에 해를 구한다.
\end{itemize}
\end{frame}
} \fi

\ifen \section{Conclusion} \else \section{해법} \fi

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack.

%The nestedness result for the $g_j = 1$ special case also resembles the knapsack problem, although the proof is more subtle.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{Conclusion}
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제에는 \textbf{이론적으로 흥미}가 있다. Submodular 최대화 문제이지만, 근사 해법 성질은 배낭 문제에 더 가깝다.

%$g_j=1$의 특수한 경우의 포함 사슬 관계 성질도 배낭 문제와 유사하며, 증명 과정은 좀 더 미묘하다.

좋은 대학 지원 전략에는 \textbf{금전적 가치}가 있다. 미국 입학 컨설컨트의 시간당 급료는 평균 200달러! ⇒ 공공 이익을 위해 코드는 open source license로 공개.

문제를 확장할 수 있는 향후 연구: 위험 회피 모수, 배분적 (가나다군) 제약 조건, 메모리 소모량 절감.
\end{frame}
} \fi

\begin{frame}{\ifen References \else 참고 문헌 \fi}
\parskip 0em
\leftskip 2em
\parindent -2em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

@@

%Fisher, Marshall, George Nemhauser, and Laurence Wolsey. 1978. ``An analysis of approximations for maximizing submodular set functions—I.'' \emph{Mathematical Programming} 14: 265--94.

@@

%Kapur, Max and Sung-Pil Hong. 2022. ``The College Application Problem.'' Preprint. \url{https://github.com/maxkapur/CollegeApplication}.

@@
